### 2019-11-12 Action letter.Rmd
Final changes before introduction

\subsection*{NOTE FROM EDITORIAL OFFICE:  We ask that you upload either Word or RTF versions of both your title page and manuscript,  rather than PDFs, when resubmitting.}

@@

We thank you and the Reviewers for your thorough comments, and for the helpful summary you've provided. We hope that you will find that our responses adequately address the issues raised, and that the quality of the work has been improved.

<!--The revised manuscript (including title page, abstract, and references) comprises 35 pages, or 8666 words. Four supplementary tables are included, whose size prohibits them from being included in the manuscript: A full correlation table (total sample and paneled by adolescent sex); the full matrix of parameter estimates; detailed scale descriptives and intercorrelations, and a full matrix of parameter estimates for an alternative analysis suggested by a Reviewer. 
Should the manuscript be accepted, we are prepared to make all syntax and results of the analyses conducted available on a public code repository referenced in the paper, to safeguard reproducibility. 
Treatment of participants was in accordance with the APA ethical principles. On behalf of the authors, I declare that I have no conflicts of interest concerning this article. I will serve as the corresponding author for this manuscript.-->

@@

We thank the Editor for pointing out the lack of consistency across sections, and we have edited the revised manuscript to resolve this issue. We now consistently use the terms "joint and relative quantitative involvement". Joint quantitative involvement is defined as the average involvement of both parents (a latent mean). Relative involvement is defined as the difference between mothers and fathers (not a ratio; a latent difference). These variables are obtained by re-expressing the variance of the two observed variables, absolute amount maternal and paternal involvement, into two latent variables, reflecting the mean and difference. We have included a Figure that presents the model visually, which should clarify this technique. We also explicitly point out, once in the Introduction and once in the Discussion, that joint involvement represents the total amount of care provided to children, whereas relative involvement captures the childcare distribution who does what).

@@

We appreciate the suggestion, and have incorporated such a figure.

@@

We have elaborated on the Table notes. We think that the definition of joint and relative involvement is adequately addressed by the increased consistency with regard to terminology, in conjunction with the new Figure - but we are happy to take further action if necessary.

@@

\RC{3d. The results section is very dense. You could make it less dense by articulating clear hypotheses at the end of the Introduction and then reporting whether those specific hypotheses were supported. As just one example, you state on p. 9, "Applying this insight from the coparenting literature, we might thus expect parents’ quantitative involvement to be directly associated with their qualitative parenting behaviors and children’s emotional adjustment, and to moderate effects between qualitative parenting behaviors and emotional adjustment." This is not a directional hypothesis, as stated. It would be helpful if you could be more specific. Are you predicting that the more time mothers and fathers spend caring for children, the more warm, consistent, etc. their parenting will be? Do you expect this to be equally true for mothers and fathers? How do you expect the quantitative measure of parenting to moderate the association between qualitative measures and children's emotional adjustment? }

@@

@@

To address this comment, we've attempted to ensure that every issue in the Introduction is paralleled in the Discussion. We have also attempted to clarify the between/within distinction. A major contribution of the present study is that we are (one of?) the first to make this distinction in this particular research area. Consequently, there is no prior literature available to base specific hypotheses about between/within effects on. The best we can do is develop exploratory hypotheses based on a conflicting literature that has lumped together between/within effects. Thus, we cannot make more specific predictions than we currently do.

@@

We appreciate this suggestion. We agree that parent effects could very well be present at even younger ages, and explicitly acknowledge this in the revision. At the same time, we think that it is interesting and potentially meaningful that parent effects - but not child effects - tend to become smaller/non significant when stable between-family differences are accounted for. We have attempted to clarify our discussion of the potential theoretical/methodological implications of this finding.

> Nowadays, it is commonly acknowledged that parents and children reciprocally influence one another. However, the methods used to demonstrate bi-directional effects have been criticized for misrepresenting the direction of effects when stable between-family differences are not accounted for [@hamakerCritiqueCrosslaggedPanel2015]. We are aware of only one prior study that controlled for stable between-family differences when examining the interplay between parenting and emotional adjustment. This study found that child effects substantially outnumbered parenting effects in adolescence [@vanlissaRoleFathersMothers2018a]. The authors explained this finding in light of the relative equality of parent-adolescent relationships. The present study casts doubt on that interpretation, as we found a preponderance of child effects between the ages of 6-12. Although it is, of course, possible that parent effects are in effect at an even younger age, we can also consider the question: To what extent are parents shaping children's development, and to what extent are they adapting to it?  
The finding that parent effects become smaller or non-significant once stable between-family differences are accounted for has also been demonstrated in other areas of developmental research (REF). As similar patterns continue to emerge, it might be worth reflecting on their implications for developmental theory. Such findings are less congruent with a fully bidirectional conceptualization of reciprocal influence, and more consistent with a model where parents "set the stage" for children's development through their stable differences from other parents, and continue to adjust to children's changing needs over time. Methodological innovations that examine the role of stable between-family differences can thus inspire more sophisticated theoretical conceptualizations of parental influences in child development.  
At the same time, we should consider the limitations of these methods. The assumption that within-family fluctuations adequately capture all causal influences that parents exert on their children, for instance, is questionable. Stable factors can also exert changing influences over time. As an illustrative example: The genetic makeup that is passed from parents to children is stable, and yet the expression of some genes emerges over time. It might similarly be possible for stable parental psychosocial characteristics to influence children differently at different time points. Another important limitation is that within-family cross-lagged effects are time scale dependent. If parents shape their children through specific behaviors in dyadic interactions, then annual reflective self-reports might fail to capture parenting effects. Thus, although these methodological innovations are undoubtedly a step forward, they might not be the definitive paradigm for investigating the interplay between parents and children.

\RC{Second, there are pronounced individual differences in how parents react to children. The same level of emotionally dysregulated behavior might elicit anger from one parent and inductive reasoning from another. There is a great deal of evidence from parenting interventions that how parents react to difficult behavior affects whether their children remain noncompliant and dysregulated or whether their behavior improves. So I think you're selling parents short if your claim is that the only way they influence their children is through the changing expression of the genes they have bequeathed them.}

We agree, and as we mention in the manuscript, we also find these between-family differences in parents' responses to childen's emotional adjustment in the present study. In the rewritten paragraphs above, we have attempted to clarify that we are not making any claims about genes, but instead, we are questioning the assumption of the RI-CLPM model that all reciprocal influences are captured by within-family fluctuation. We then introduce genes as an illustrative example of something very stable that can nonetheless have changing influences over the life course. In the revision, we have emphasized that this is an illustrative example, and we then draw a parallel to how stable psychosocial traits might similarly have changing effects over the course of development.

@@

We operationalized emotional adjustment in terms of the emotional adjustment subscale of the SDQ. Consequently, we cite the scale validation paper of the SDQ here. It is not evident to us what other reference would be more appropriate than the one we used to operationalize this construct, but if the Reviewer feels that a particular citation should be included, we are happy to do so.

\RC{1.2c ...introduce the idea that mothers and fathers may plan a unique role in the development of emotional adjustment, before focusing in on the role of fathers. Finally, it would help the reader to provide the research goals in the first 1-2 pages of the introduction to get a sense where the paper is headed.}

@@

@@

Thank you for pointing out that sex differences are omitted from the list of contributions mentioned in *The Present Study*. We have attempted to address this issue by adding sex differences to the list, and we have also clarified our specific hypotheses regarding sex differences in the preceding paragraph.

> We therefore hypothesize that parents will display more responsiveness, structure, and inductive reasoning towards girls, and more negative parenting towards boys. Furthermore, we predict stronger associations between qualitative parenting and emotional adjustment between children and the same-sex parent.  
*[...]*
Consequently, we have no hypothesis regarding sex differences in children's average levels of emotional adjustment.  
*[...]*
Finally, we examined sex as a moderator of between-family differences in all study variables and within-family predictive effects

@@

We agree wholeheartedly with this point, and we had formulated hypotheses for all patterns studied, but we understand that our colloquial use of language made it hard to identify our specific hypotheses. For example, in the original manuscript, we wrote:

> Applying this insight from the coparenting literature, we might thus expect parents' quantitative involvement to be directly associated with their qualitative parenting behaviors and children's emotional adjustment, and to moderate effects between qualitative parenting behaviors and emotional adjustment.

In the revision, we have attempted to address this comment by being more specific. Now, this section reads:

> Applying this insight from the coparenting literature, we thus hypothesize that  parents' quantitative involvement will be directly associated with their qualitative parenting behaviors and children's emotional adjustment, and will moderate effects between qualitative parenting behaviors and emotional adjustment.

There is a bit of a challenge, however: Because there is no precedent for using the random-intercept cross-lagged panel model or its multilevel DSEM extension in the literature on parental involvement and emotional adjustment, there is no literature upon which to base such hypotheses. Therefore, the best we can do is to present *conceptual* hypotheses.

@@

This might be an oversight, as all of this information requested is provided in Supplementary Table 1 (*Scale descriptive statistics are provided in Supplementary Table 1*). Perhaps these supplementary Tables are not automatically shared with reviewers?

To address this comment, we've clarified this sentence in the manuscript, which now reads: *Scale descriptive statistics, number of items, number of complete cases, and reliability are reported in Supplementary Table 1*. We also reproduce Table S1 here, in case the Reviewer does not have access:

@@

We have followed the convention of 1) providing example items as an indication of face validity, and 2) citing the scale validation papers for more information on predictive validity. We would like to defer to the Editor as to whether further actions need to be taken (we are also not sure what these actions would be).

@@

Several working papers have been written on the recruitment, participants, data collection, etc. for this sample. However, this information was masked in the original manuscript, to enable blind peer review. However, as both Reviewers and the Editor requested access to these references to evaluate the study quality, we have now unmasked these sections in the revised manuscript:

@@

All of our results are reported in terms of correlations (which, when squared, gives the proportion of explained variance shared by two variables) and standardized regression coefficients (a one SD increase in X predicts a $\beta$ SD increase in Y, conditional on the other predictors), both of which are already effect sizes [@nieminenStandardisedRegressionCoefficient2013].

*Probably, we should cite the values in the text, as the Editor also suggested.*

@@

We have attempted to address this comment by labeling and annotating the Tables more extensively.

@@

In the original manuscript, we explained how sex differences were tested in the strategy of analyses:

@@

In the revision, we have attempted to further clarify this by including a visual representation of the model, and by labeling Tables more clearly.

@@

We appreciate this suggestion! Strictly speaking, since Bayesian analyses focus on estimation rather than inference, it is correct to say that the (maximum a-posteriori) estimate is different between mothers and fathers, without further substantiation - because in the Bayesian framework, the maximum a-posteriori estimate can be interpreted as the most likely population value for the parameter, conditional on the data and prior. In practice, since we use Bayesian estimation for pragmatic reasons, we understand that there is added value in knowing the posterior distribution of the difference between mothers and fathers.

Therefore, to address this comment, we have re-run all analyses to obtain the posterior for the differences between mothers and fathers. We have reported this information in-text whenever making a statement about mother/father differences, and have added it to the relevant Supplementary Tables with the full model parameters. We have omitted it from the smaller Tables in the manuscript, because their function is to help make it easier for readers to digest the results, and we feel that adding four columns with difference tests would interfere with that goal.

@@

@@

We completely agree with the Reviewer that warmth and security, provided by either parent, are positively related to emotional adjustment development. We discuss this in REFER TO PARAGRAPH. It appears that the Reviewer interpreted the word *uniquely* to mean that *only* fathers contribute to emotional adjustment. We intended to say that fathers contribute in a *different* way from mothers.   
We merely intended to summarize fatherhood theory regarding the distinction between the attachment vs activation relationship: An often-cited theory that implies that demandingness is a more important socialization mechanism for fathers than for mothers, and that warmth is a more important socialization mechanism for mothers than for fathers.

In the Revision, we have attempted to address the Reviewer's comment by disambiguating this section, which now reads:

\AlmostDone

@@

We have capitalized the word after a colon if it is the beginning of an independent clause, in line with the the sixth edition of the APA Publication Manual. We would generally to prefer to adhere to the Publication Manual in these matters, but we defer to the Editor as to whether further changes are required. To address this typo, and other spelling errors, we have checked the manuscript with the R-package `hunspell` and fixed about 10 other errors.

@@

<!--[RK14]Socialization; children model their parents and see that their parents are also not able to regulate their emotions??-->

@@

<!-- [RK15]The worse children fare, the more parents want to correct them/put them in line? -->
\WorkInProgress

@@

@@

1. We have clarified this section in the discussion.
2. We have removed masking of sample details.

The Discussion section in question now reads:

> One recent study with a similar design to the present study found that child effects substantially outnumbered parenting effects, and speculated that this might be due to the greater equality of parent-adolescent relationships, compared to earlier childhood [@vanlissaRoleFathersMothers2018a]. The present study casts doubt on this speculation, as we found that child effects outweighed parenting effects, even at a young age. The fact that both the present study and this previous work found a preponderance of child effects, despite the different age ranges of the samples, invites the question: Are parents really shaping children's development, or are they, instead, adapting to it?

@@

>>>>

@@

We thank you and the Reviewers for your thorough comments, and for your helpful summary of these comments. We have attempted to address all comments, and hope that you will find that the quality of the work has been improved.

With regard to the Editorial Office's request that we upload a Word or RTF file: In line with the Submission Guidelines on the Developmental Psychology website, we have provided \latex as a `zip`-file, with accompanying `.pdf`. We do not have a Word version of this manuscript available. We could manually convert this to Word, but the typographical advantages of using Latex would then be lost. Please let us know how to proceed.

@@

We thank the Editor for pointing out the lack of consistent terminology across sections, and we have edited the revised manuscript to resolve this issue. We now consistently use the terms "joint and relative quantitative involvement". Joint quantitative involvement is defined as the average involvement of both parents (a latent mean). Relative involvement is defined as the difference between mothers and fathers (not a ratio; a latent difference). These variables are obtained by re-expressing the variance of the two observed variables, absolute amount maternal and paternal involvement, into two latent variables, reflecting the mean and difference. We have included a Figure that presents the model visually, which should clarify this technique. We also explicitly point out, once in the Introduction and once in the Discussion, that joint involvement represents the total amount of care provided to children, whereas relative involvement captures the childcare distribution who does what).

@@

We appreciate the suggestion, and have incorporated this Figure, see below:

```{r figure1, out.width="100%", fig.cap="T-1: previous measurement occasion. ri: random intercept. s: random slope. M: Mother's qualitative involvement. E: Emotional adjustment. F: Father's qualitative involvement. inv: quantitative involvement. Thus, sME represents the random slope of Mothers' qualitative involvement on emotional adjustment."}
knitr::include_graphics("Figure1.png")
```

@@

As requested, we have elaborated and clarified the Table notes in the revision. Regarding the definition of joint and relative involvement - we believe that this is adequately clarified by the consistent use of terminology in the revised manuscript, and the new Figure describing the model specification - but we are happy to take further action if necessary.

@@

We have attempted to address this comment by adding extensive Table notes and clarifying in-table text throughout the *Results* section. We assume that readers are familiar with the interpretation of correlations, and have therefore not further clarified the interpretation of correlations. With regard to the standardized regression coefficients (and their variance), we have included an elaborate explanation of the interpretation of the first standardized regression coefficient reported for readers not familiar with standardized regression coefficients. For the sake of saving space, we do not interpret each coefficient so elaborately (we prefer to stick with the APA publication manual, and report results either in-text or in a table, but not both). We explain the basic random effects once, and the moderated effects once.

The added sections for the random effects reads:

> At the within-family level, we examined over-time predictive effects between qualitative parenting and emotional adjustment. The intercepts of these random effects reflect the average standardized regression coefficient across families. The variances in Table 2 indicate whether this coefficient differs in strength (and sign) between families. We report unstandardized variances, because the standardized variances are, by definition, set to 1. With regard to within-families parenting effects, we found no evidence for hypotheses $H_{1b-d}$, as none of the intercepts differed significantly from zero. In line with hypothesis $H_{1a}$, however, on average, a maternal warmth positively predicted children's emotional adjustment in the next wave. The standardized regression coefficient of this effect, and others, is interpreted as follows: A $.99$ standard deviation increase in children's emotional adjustment in the next wave (see Table 2).

The added section for the moderation effects reads:

> To examine interactions between involvement quality and quantity, we examined standardized regression coefficients of between-family differences in quantitative involvement on within-family cross-lagged effects between qualitative parenting behaviors and emotional adjustment (Table 3). With regard to the moderation of parenting effects, the only significant effects we found were for maternal warmth. Specifically, a one-standard deviation increase in joint involvement predicted a decrease in the within-families predictive effect of maternal warmth on emotional adjustment of $-.14$ of a standard deviation of the effect (see Table 2).

\RC{3d. The results section is very dense. You could make it less dense by articulating clear hypotheses at the end of the Introduction and then reporting whether those specific hypotheses were supported. As just one example, you state on p. 9, "Applying this insight from the coparenting literature, we might thus expect parents’ quantitative involvement to be directly associated with their qualitative parenting behaviors and children’s emotional adjustment, and to moderate effects between qualitative parenting behaviors and emotional adjustment." This is not a directional hypothesis, as stated. It would be helpful if you could be more specific. Are you predicting that the more time mothers and fathers spend caring for children, the more warm, consistent, etc. their parenting will be? Do you expect this to be equally true for mothers and fathers?}

We have attempted to address this comment by clarifying and labelling our hypotheses, and re-structuring the *Introduction*, *Results*, and *Discussion* sections to follow the order of these hypotheses. The hypotheses are:

* $H_{1a-d}$ Warmth, consistency, and inductive reasoning will be positively, and anger negatively, associated with children's emotional adjustment
* $H_{2a-d}$ Emotional adjustment will positively predict parental warmth, and negatively predict consistency, inductive reasoning, and anger
* $H_{3}$ Emotional adjustment will be more strongly associated with maternal warmth and anger, and with paternal demanding behaviors, such as consistency and inductive reasoning
* $H_{4a-d}$ Greater joint involvement will positively attenuate both parents' desirable parenting behaviors (warmth, consistency, and inductive reasoning), and negatively attenuate parental anger
* $H_{5a-d} Greater differential involvement would attenuate the desirable parenting behaviors of the more involved parent positively, and those of the less involved parent negatively
* $H_{6a}$ Greater joint care should positively predict children's emotional adjustment
* $H_{6b}$ Greater relative involvement will negatively predict emotional adjustment
* $H_{7a-d}$ Parents will display more warmth, consistency, and inductive reasoning towards girls than boys, and more anger towards boys than girls
* $H_{8a-d}$ Associations between qualitative parenting and emotional adjustment will be stronger between children and their same-sex parent

\RC{3e How do you expect the quantitative measure of parenting to moderate the association between qualitative measures and children's emotional adjustment? }

Because such interactions have not been examined before, any hypothesis would be unsubstantiated. Thus, our work in this area is exploratory. We now acknowledge this explicitly:

> Interactions between involvement quality and quantity have largely been overlooked in the parenting literature [@jaffeeLifeFatherBenefits2003]. Consequently, it is not possible to substantiate specific hypotheses for such interactions. [...] We thus explored the moderating effects of joint and relative quantitative involvement on the interplay between qualitative parenting behaviors and emotional adjustment.

@@

As mentioned in our response to the Editor's comment 3d, we have now re-written several sections of the paper, including the *Discussion*, to follow the same structure, guided by the (numbered) hypotheses.

@@

This issue is also partly addressed by our efforts to ensure that the structures of the *Introduction*, *Results* section, and *Discussion* are parallel. We have also attempted to clarify why it is important to use methods that disentangle between/within variance:

> Methods commonly used to examine direction of effects between parents and children have been criticized for yielding biased results if stable between-family differences are not controlled [@hamakerCritiqueCrosslaggedPanel2015]. Innovative methods provide better estimates of dynamic reciprocal processes within families, by controlling for stable between-family differences: The recently developed random-intercept cross-lagged panel model, which is an extension of the standard cross-lagged panel model [@hamakerCritiqueCrosslaggedPanel2015], and dynamic structural equation modeling (DSEM); a multilevel generalization of this model [@asparouhovDynamicStructuralEquation2018].

A major contribution of the present study is that we are (one of?) the first to make this distinction in this particular research area. Consequently, there is no prior literature available to base specific hypotheses about between/within effects on. The best we can do is develop exploratory hypotheses based on literature that has lumped together between/within effects. In the revision, we have attempted to explain why we cannot make (more) specific predictions about when we expect to see between-family effects or within-family effects:

> Several studies have re-examined the direction of effects between parents and children using these methods [...] These two studies also illustrate that applying these new methods changes the pattern of results in unexpected ways. Consequently, it is impossible to make specific predictions about the pattern of between-family correlations and within-family predictive effects. For now, we will assume that $H_{1a-d}$ and $H_{2a-d}$ apply at both the between- and within-family level.

@@

We appreciate this suggestion. In the revision, we explicitly acknowledge that parent effects could very well be present at even younger ages:

> In the area of parenting and emotional adjustment development, we are aware of only one prior study that controlled for stable between-family differences, and similarly reported mostly child effects and between-family level correlations in a sample of adolescents [@vanlissaRoleFathersMothers2018a]. The authors explained their findings by proposing that child effects might be more common in adolescence than in childhood, because parent-adolescent relationships are more egalitarian at that age. They argued that the between-family level correlations might reflect the consolidated influence of within-family parent effects that occurred at an earlier age. The fact that the present study similarly found a preponderance of child effects and between-family level correlations in a sample of younger children, age 6-12, suggests that __either parent effects occurred at an even younger age__, or that something else is at play.

\RC{4d. Second, there are pronounced individual differences in how parents react to children. The same level of emotionally dysregulated behavior might elicit anger from one parent and inductive reasoning from another. There is a great deal of evidence from parenting interventions that how parents react to difficult behavior affects whether their children remain noncompliant and dysregulated or whether their behavior improves.}

We agree, and as mentioned in the manuscript, we also find these between-family differences in parents' responses to childen's emotional adjustment in the present study:

> The variances of all parenting effects were significant, indicating that the effect of qualitative parenting behaviors on children's emotional adjustment varies across families. [...] The variances of all child effects were all significant but small, indicating that the effect of children's emotional adjustment on their parents' child-rearing behaviors differs somewhat between families.

\RC{4e. So I think you're selling parents short if your claim is that the only way they influence their children is through the changing expression of the genes they have bequeathed them.}

This is certainly not a claim we intend to make, and we have rewritten the paragraph in question to clarify that we are not making any claims about genes, but instead, we are questioning the assumption of the RI-CLPM model that all reciprocal influences are captured by within-family fluctuation. We then introduce genes as an illustrative example of something very stable that can nonetheless have changing influences over the life course. In the revision, we have emphasized that this is an illustrative example, and we then draw a parallel to how stable psychosocial traits might similarly have changing effects over the course of development:

> At the same time, we should consider the limitations of these methods. The assumption that within-family fluctuations adequately capture all causal influences that parents exert on their children, for instance, is questionable. Stable factors can also exert changing influences over time. As an illustrative example: The genetic makeup that is passed from parents to children is stable, and yet the expression of some genes emerges over time. It might similarly be possible for stable parental psychosocial characteristics to influence children differently at different time points.

@@

We operationalized emotional adjustment in terms of the emotional adjustment subscale of the SDQ, and cite the SDQ validation paper. It is not evident to us what other reference would be more appropriate than the one we used to operationalize this construct, but if the Reviewer feels that specific literature should be cited, we are happy to do so.

\RC{1.2c ...introduce the idea that mothers and fathers may plan a unique role in the development of emotional adjustment, before focusing in on the role of fathers...}

\RC{1.2d ...Finally, it would help the reader to provide the research goals in the first 1-2 pages of the introduction to get a sense where the paper is headed.}

@@

We appreciate the suggestion; indeed, the idea that both quantitative and qualitative involvement are important (and might interact) is most important. The rough division along disciplinary lines is interesting, but not central to the argument. We have therefore edited our argumentation to focus on the importance of jointly investigating quantitative and qualitative involvement, and removed all references to disciplinary differences.

@@

This issue is partly addressed by our efforts to ensure that the structures of the *Introduction*, *Results* section, and *Discussion* are parallel. Furthermore, we have added sex differences to the list of contributions in *The present study* (*"we examined child sex as a moderator of between-family differences in all study variables and within-family predictive effects"*), and we have also formulated our specific hypotheses regarding sex differences in the preceding paragraph.

> We therefore hypothesize that parents will display more warmth, consistency, and inductive reasoning towards girls than boys, and more anger towards boys than girls, $H_{7a-d}$. Furthermore, we predict stronger associations between qualitative parenting and emotional adjustment between children and their same-sex parent, $H_{8a-d}$.
*[...]*
Consequently, we have no hypothesis regarding sex differences in children's average levels of emotional adjustment.

@@

We have attempted to address this comment by clarifying and labelling our hypotheses, and re-structuring the *Introduction*, *Results*, and *Discussion* sections to follow the order of these hypotheses. The hypotheses are:

* $H_{1a-d}$ Warmth, consistency, and inductive reasoning will be positively, and anger negatively, associated with children's emotional adjustment
* $H_{2a-d}$ Emotional adjustment will positively predict parental warmth, and negatively predict consistency, inductive reasoning, and anger
* $H_{3}$ Emotional adjustment will be more strongly associated with maternal warmth and anger, and with paternal demanding behaviors, such as consistency and inductive reasoning
* $H_{4a-d}$ Greater joint involvement will positively attenuate both parents' desirable parenting behaviors (warmth, consistency, and inductive reasoning), and negatively attenuate parental anger
* $H_{5a-d} Greater differential involvement would attenuate the desirable parenting behaviors of the more involved parent positively, and those of the less involved parent negatively
* $H_{6a}$ Greater joint care should positively predict children's emotional adjustment
* $H_{6b}$ Greater relative involvement will negatively predict emotional adjustment
* $H_{7a-d}$ Parents will display more warmth, consistency, and inductive reasoning towards girls than boys, and more anger towards boys than girls
* $H_{8a-d}$ Associations between qualitative parenting and emotional adjustment will be stronger between children and their same-sex parent

@@

We respectfully believe that this comment might be the result of an oversight, or of a misunderstanding on our part with regard to what information is relayed to Reviewers.
All of this information was provided in Supplementary Table 1, as mentioned in the manuscript: *Scale descriptive statistics are provided in Supplementary Table 1*. Perhaps these supplementary Tables are not automatically shared with reviewers?

To address this comment, we've clarified this sentence in the manuscript, which now reads: *Scale descriptive statistics, number of items, number of complete cases, and reliability are reported in Supplementary Table 1*. We also reproduce Table S1 here, in case the Reviewer does not have access. Hopefully this addresses the issue.

@@

We have followed the convention of 1) providing example items as an indicator of face validity, and 2) citing the scale validation papers for more information on predictive validity. We would like to defer to the Editor as to whether further actions need to be taken (we are also not sure what these actions would be).

@@

The recruitment, participants, data collection, etc. for this sample are well-documented and these protocols are public. This information was masked in the original manuscript, to enable blind peer review. However, as both Reviewers and the Editor requested access to these references to evaluate the study quality, we have now unmasked these sections in the revised manuscript:

@@

All of our results are reported in terms of correlations and standardized regression coefficients, both of which are already effect sizes [@nieminenStandardisedRegressionCoefficient2013]. We agree with the Reviewer that this was not communicated clearly enough, however, so we have attempted to address this comment by clarifying in the text and in the Tables that these results are reported as correlations and standardized regression coefficients. We assume that all readers are familiar with the interpretation of correlation coefficients, but we have included two detailed examples of the interpretation of standardized regression coefficients in the context of basic random effects, and moderated effects.

The added sections for the random effects reads:

> At the within-family level, we examined over-time predictive effects between qualitative parenting and emotional adjustment. The intercepts of these random effects reflect the average standardized regression coefficient across families. The variances in Table 2 indicate whether this coefficient differs in strength (and sign) between families. We report unstandardized variances, because the standardized variances are, by definition, set to 1. With regard to within-families parenting effects, we found no evidence for hypotheses $H_{1b-d}$, as none of the intercepts differed significantly from zero. In line with hypothesis $H_{1a}$, however, on average, a maternal warmth positively predicted children's emotional adjustment in the next wave. The standardized regression coefficient of this effect, and others, is interpreted as follows: A $.99$ standard deviation increase in children's emotional adjustment in the next wave (see Table 2).

The added section for the moderation effects reads:

> To examine interactions between involvement quality and quantity, we examined standardized regression coefficients of between-family differences in quantitative involvement on within-family cross-lagged effects between qualitative parenting behaviors and emotional adjustment (Table 3). With regard to the moderation of parenting effects, the only significant effects we found were for maternal warmth. Specifically, a one-standard deviation increase in joint involvement predicted a decrease in the within-families predictive effect of maternal warmth on emotional adjustment of $-.14$ of a standard deviation of the effect (see Table 2).

@@

We have attempted to address this comment by labeling and annotating the Tables more extensively, and by explaining the coefficients in-text, as illustrated in our response to the previous question.

@@

In the original manuscript, we explained how sex differences were tested in the strategy of analyses (see fragment below), and in the revision, we have attempted to further clarify this by including a visual representation of the model (Figure 1), and by labeling Tables more clearly.

@@

@@

We appreciate this suggestion! We appreciate this suggestion! To address this comment, we have re-run all analyses to obtain the posterior for the differences between corresponding parent- and child effects. We have explained this procedure in the text (fragment cited below), and have added it to Table 2 in the form of labels that indicate which parameters differed significantly, and we have reported the full difference tests in Supplementary Table S5. These difference tests do not alter the interpretation of most results, because they closely mirror the pattern of significant/non-significant effects for fathers in comparison to mothers: All but one of the effects that are significant for one parent, but non-significant for the other parent, have significant difference tests. The exception is the child effect on parental anger.

Section in Results:

> We examined differences between fathers and mothers in parent- and child effects the same way [by testing the significance of the difference between corresponding mother- and father effects (see Table 2 and Supplementary Table S5)]. All effects that were significant for one parent but not significant for the other parent had significant difference tests, except for the child effect of emotional adjustment on parental anger, which did not differ significantly between parents.

Table note:

> Matching letters indicate that parameters differed significantly, see Supplementary Table S5.

@@

This is automatically done by the typesetting program, to space the text evenly, but we have attempted to override the behavior.

@@

We completely agree with the Reviewer that warmth and security, provided by either parent, are positively related to emotional adjustment development. It appears that the Reviewer interpreted the word *uniquely* to mean that *only* fathers contribute to emotional adjustment. We intended to say that fathers contribute in a *different* way from mothers. Specifically, the effect of specific parenting behaviors might be a bit stronger for mothers versus fathers. In the Revision, we have attempted to address the Reviewer's comment by disambiguating this section, which now reads:

> Fathers' qualitative involvement is associated with emotional adjustment, even after accounting for mothers' qualitative involvement [@flouriFathersBehaviorsChildren2010]. Although some research suggests that both parents influence children similarly [@lambDevelopmentSignificanceFatherChild2004; @faganShouldResearchersConceptualize2014], there is also evidence for unique contributions of mothers and fathers. Some have theorized that mothers and fathers might fulfill somewhat specialized roles [@bogelsDoesFatherKnow2011]. In line with the theoretical notions of "attachment" and "activation" relationships, mothers tend to encourage and respond supportively to emotional expression to a greater extent than fathers, whereas fathers structure and sanction emotion expressions more than mothers [@cassanoInfluenceGenderParental2007; @eisenbergParentalReactionsChildren1999]. Moreover, for adolescents' emotional adjustment, maternal warmth was found to be a more salient socialization mechanism than demandingness, whereas this pattern was reversed for fathers [@vanlissaRoleFathersMothers2018a]. Similar differentiated associations were also found for younger children's psychological adjustment [@mcdowellDifferencesMothersFathers2003]. Finally, there is some evidence that emotional adjustment is more negatively impacted by mothers' negative parenting, compared to fathers [@changHarshParentingRelation2003]; perhaps because negative parenting is incongruous with the notion of the maternal "attachment" relationship. We might therefore hypothesize that emotional adjustment would be more strongly associated with maternal warmth and anger, and with paternal demanding behaviors, such as consistency and inductive reasoning, $H_{3}$.

@@

We have capitalized the word after a colon if it is the beginning of an independent clause, in line with the APA Publication Manual (sixth edition). We would generally prefer to adhere to the Publication Manual in these matters, but we defer to the Editor as to whether further changes are required. To address this typo, and other spelling errors, we have checked the manuscript with the R-package `hunspell` and fixed about 10 other errors.

@@

Parental anger undermines emotional adjustment because anger is upsetting to children, and because parental anger reflects poor emotional adjustment on the parent's side, which children copy. We have rewritten the section to clarify this point:

> Negative parenting, which we operationalized as parental anger, is an additional qualitative parenting dimension that is negatively linked with children's emotional adjustment [@changHarshParentingRelation2003; @eisenbergParentalReactionsChildren1999]. 
Parental anger expressions negatively impact children's emotional adjustment [@scaramellaParentingChildrenDistress2008], because parental anger is upsetting, and because anger reflects poor parental emotion regulation, which serves as a model for children [@changHarshParentingRelation2003].

@@

We have completely rewritten this section, as we agree that it was confusing. Basically, the literature supports the notion that warmth, consistency, and inductive reasoning are positively associated, and anger is negatively associated, with emotional adjustment. However, research focusing on *behavioral control*, a different aspect of demandingness that we did not measure, is more equivocal. Some studies have found positive associations with emotional adjustment, and others have found negative associations - particularly in terms of child effects. We had tried to convey this subtlety in the original manuscript, but we have now removed it, because it is confusing, and because it is only tangentially relevant, because we did not measure behavioral control. The section now reads:

> [...] bi-directional effects are not routinely investigated in the childhood literature [@flouriFathersBehaviorsChildren2010]. Consequently, most of the research cited in support of hypotheses $H_{1a-d}$ is cross-sectional, and could be taken as support for child effects as well as parent effects. We therefore hypothesize that child effects are similar in direction, and that warmth, consistency, and inductive reasoning positively predict, and anger negatively predicts, emotional adjustment, $H_{2a-d}$. This is supported by studies that investigated child effects specifically, and found that children's maladjustment elicits less parental warmth, and more negative parenting [@gadeyneLongitudinalRelationsParenting2004]. Bi-directional positive links between parental consistency and emotional adjustment have also been reported [@lenguaBidirectionalAssociationsTemperament2005]. 
The adolescent literature provides additional evidence that emotional adjustment positively predicts parental support [@otterpohlCrossLaggedRelationsParenting2015; @vandergiessenPerceivedAutonomySupport2014], and negatively predicts negative parenting [@wijsbroekDirectionEffectsPerceived2011]. Thus, in a way, parents respond positively to emotional adjustment, and negatively to maladjustment.

@@

We have done as asked. Nearly every instance of "sex" has been replaced by "child sex", except where the fact that we are discussing child sex is made clear in the rest of the sentence.

@@

1. We have removed masking of sample details.
2. We have clarified this section in the discussion, which now reads:

> we are aware of only one prior study that controlled for stable between-family differences, and similarly reported mostly child effects and between-family level correlations in a sample of adolescents [@vanlissaRoleFathersMothers2018a]. The authors explained their findings by proposing that child effects might be more common in adolescence than in childhood, because parent-adolescent relationships are more egalitarian at that age. They argued that the between-family level correlations might reflect the consolidated influence of within-family parent effects that occurred at an earlier age. The fact that the present study similarly found a preponderance of child effects and between-family level correlations in a sample of younger children, age 6-12, suggests that either parent effects occurred at an even younger age, or that something else is at play.

@@

We have attempted to address this comment by adding extensive Table notes and clarifying in-table text throughout the *Results* section. Some of the results are presented as correlation coefficients. We assume that readers are familiar with the interpretation of correlations, and have therefore not further clarified these sections. The remaining results are presented as standardized regression coefficients. Some of these vary between families, and thus have a random intercept and a variance. We have included an elaborate explanation of the interpretation of the first random intercept for the within-family standardized regression coefficients, and one elaborate example for the interpretation of the moderated effects.

The added sections for the random effects reads:
